---
title: "Lab Test 2"
author: "Sean Park"
date: '2021 8 23 '
output: word_document
---
1.

a) The probability is 0.15
```{r}
pnorm(2500,3020,502)
```

b) The probability is 0.75.
```{r}
pnorm(2500,3020,502)*5
```

c) i) H0 = The probability of underweight baby born is not changed.            (Pr(X < 3020) = 0.5)
      H1 = THe probability of underweight baby born is decreased.  
           (Pr(X < 3020) < 0.5)
      
  ii) p-value is 0.026.
```{r}
pbinom(180,400,0.5)
prop.test(180,400,0.5, alternative="less", conf.level = 0.95)
```

  iii) Since the p-value is less than 0.05. We reject null                hypotheses. Therefore the proportion of underweight baby born       statistically decreased in 95% confidence level.
      
   iv)Based on the sample, the proportion of underweight babies should be between 0.401 and 0.499 in 95% confidence level.Confidence interval does not contain null hypothesis value 0.5. 
```{r}
t.score = qt(0.025,399,lower.tail = FALSE)
pi.hat.obs = 180/400
pi.hat.se = sqrt((pi.hat.obs*(1-pi.hat.obs))/400)
lower.95CI.bound = pi.hat.obs-(t.score*pi.hat.se)
upper.95CI.bound = pi.hat.obs+(t.score*pi.hat.se)
print(lower.95CI.bound)
print(upper.95CI.bound)
```
      
      
      
2.

a) observed odds of diabetes for males is 0.05.
```{r}
pi.male = 4000/84000
odds.male = pi.male/(1-pi.male)
odds.male
```
      
b) observed odds of diabetes for female is 0.04
```{r}
pi.female = 3000/78000
odds.female = pi.female/(1-pi.female)
odds.female
```
      
c) odds ratio of diabetes for males to female is 1.25
```{r}
odds.ratio = odds.male/odds.female
odds.ratio
```

d) For testing the odds of getting diabetes is greater for male and   female.   Our H0 = ϕ = odds.male/odds.female = 1
          and H1 = ϕ = odds.male/odds.female > 1
  This equivalent to 
              H0 = log(ϕ) = log(odds.male/odds.female) = 0
              H1 = log(ϕ) = log(odds.male/odds.female) > 0
  In this case if we reject null hypothesis and take alternative than it    will prove that odds for male is greater.
  
  Assume the natural logarithm of the estimator of the odds ratio is approximate Gaussian distribution.
```{r}
phi.hat.obs = odds.ratio
number.male = 84000
number.female = 78000
pi.hat.obs = (4000+3000)/(84000+78000)
log(phi.hat.obs)
log.phi.hat.ster = sqrt(1/(number.male*pi.hat.obs*(1-pi.hat.obs))+1/(number.female*pi.hat.obs*(1-pi.hat.obs)))
log.phi.hat.ster
log.phi.hat.obs = log(phi.hat.obs)
p.value = pnorm(log.phi.hat.obs,0,log.phi.hat.ster,lower.tail = FALSE)
p.value
```
```{r}
curve(dnorm(x,0,log.phi.hat.ster), from=-0.25, to=0.25)
abline(v = log.phi.hat.obs)
```
  Since we have almost 0 of p-value, we reject our H0 at conventional significance level(5%). The data provides evidence that the true odds ratio of getting diabetes for males to compared to females is not one. Given the point estimate for odds ratio, it may tell us that males has higher chance to get diabetes than female. It needs further investigation.
  
  
  e) 
```{r}
log.phi.hat.se.ci = sqrt(1/4000 + 1/80000 + 1/3000 + 1/75000)
UL = log.phi.hat.obs + 1.96*log.phi.hat.se.ci
LL = log.phi.hat.obs - 1.96*log.phi.hat.se.ci
exp(c(LL,UL))
```
    Calculating the standard error using the short-cut formula and apply 95% confidence interval gives us (1.19,1.31). We are 95% confident that this interval contains the true odds-ratio of diabetes for males to females. Therefore, males are more likely to get diabetes than females.
    
      
      